Automatic Matching of Bullet Lands

### 2016-08-08 revision/response.Rmd

---
title: "Response to reviewers"
author: "Eric Hare, Heike Hofmann, Alicia Carriquiry"
date: "August 8, 2016"
output:
  pdf_document: default
bibliography: references.bib
---

### 2016-10-07 imaging-paper.Rnw
New data directory and updated paper compilation

\linenumbers
%\tableofcontents
%\newpage
<<setup, fig.keep='all', cache=FALSE, echo=FALSE, eval=TRUE, message=F, warning=F>>=
#rm(list=ls())
#wd <- getwd()
library(extrafont)
library(knitr)
imgdir <- "Figure/"
codedir <- "code"
datadir <- "app/images/Hamby252_3DX3P1of2/"

options(replace.assign=TRUE,scipen=3, digits=2)
bstats <- read.csv("data-25-25/bullet-stats-old.csv")

@@

%' \hh{XXX Do we need the next example? We could save some space here XXX}
%' Figure~\ref{fig:loessfits} shows the signatures of all lands of bullet 2 (in grey) fired from the same barrel as bullet~1. The darker line overlaid on each of the signatures, shows signature from bullet~1-5. 
%' %We can reproduce a similar figure to the one from the circular fits by overlaying the residuals from each loess fit for bullet 2 onto an image of the loess residuals from bullet~1-5. This is shown in Figure~\ref{fig:loessfits}. 
%' Bullet 2-1 is the best match for bullet~1-5, but the alignment is not quite  correct. \hh{This is one of the issues we are addressing next.}
%' 
%' \begin{figure}[hbtp]
%'   \centering
%' <<loessfits, echo=FALSE, fig.width=10, fig.height=5, out.width='\\textwidth', warning=FALSE>>=
%' br121.groove <- get_grooves(br121_bullet)
%' br122.groove <- get_grooves(br122_bullet)
%' br123.groove <- get_grooves(br123_bullet)
%' br124.groove <- get_grooves(br124_bullet)
%' br125.groove <- get_grooves(br125_bullet)
%' br126.groove <- get_grooves(br126_bullet)
%' 
%' my.loess1 <- fit_loess(br121_bullet, br121.groove)
%' my.loess2 <- fit_loess(br122_bullet, br122.groove)
%' my.loess3 <- fit_loess(br123_bullet, br123.groove)
%' my.loess4 <- fit_loess(br124_bullet, br124.groove)
%' my.loess5 <- fit_loess(br125_bullet, br125.groove)
%' my.loess6 <- fit_loess(br126_bullet, br126.groove)
%' 
%' my.loessactual <- fit_loess(br111_bullet, br111.groove)
%' 
%' minrows <- min(length(my.loess1$data$resid),
%'                length(my.loess2$data$resid),
%'                length(my.loess3$data$resid),
%'                length(my.loess4$data$resid),
%'                length(my.loess5$data$resid),
%'                length(my.loess6$data$resid),
%'                length(my.loessactual$data$resid))
%' 
%' my.df <- data.frame(y = my.loess1$data$y[1:minrows], resid1 = my.loess1$data$resid[1:minrows],
%'                     resid2 = my.loess2$data$resid[1:minrows], resid3 = my.loess3$data$resid[1:minrows],
%'                     resid4 = my.loess4$data$resid[1:minrows], resid5 = my.loess5$data$resid[1:minrows],
%'                     resid6 = my.loess6$data$resid[1:minrows])
%' 
%' melt.df <- my.df %>%
%'     gather(key = part, value = resid, resid1:resid6)
%' melt.df$part <- gsub("resid", "", melt.df$part)
%' 
%' actual.df <- my.loessactual$data[1:minrows,]
%' melt.df$land <- melt.df$part
%' qplot(y, resid, data=melt.df, #colour=factor(x), 
%'       geom="line", size=I(.75), colour=I("grey70")) + 
%'   facet_wrap(~land, ncol=3, labeller="label_both") + 
%'   scale_colour_brewer(palette="Paired") +
%'   theme_bw() + theme(legend.position="bottom") + 
%'   geom_line(data = actual.df, aes(y, resid), colour="black", size=.75, alpha=0.5) + ggtitle("Signatures of bullet 1 in grey, bullet 1-5 in black") + 
%'   ylab("Residuals of loess fit") +
%'   theme(plot.margin = unit(c(0,0,0,0), unit="cm"))
%' @    
%' \caption{\label{fig:loessfits} Residuals of a loess fit to bullets 1 and 2 from barrel 1. Bullet~1-5 is shown in black. }
%' \end{figure}
%'

@@

\begin{figure}[hbtp]
  \centering
<<crosscuts-vary-b31, echo=FALSE, fig.width = 12, fig.height = 7, out.width = '\\textwidth', cache=TRUE, warning = FALSE>>=
paths <- file.path(datadir, dir(datadir))
paths <- paths[grep(" ", paths)]

@@

\begin{figure}[hbtp]
\begin{subfigure}[t]{\textwidth}\centering
\caption{Maximal number of CMS between unknown bullet C-3 and all of the other 118 considered (known) lands. For two lands the number of maximum CMS is high. }
<<cms, echo=FALSE, fig.width=7, fig.height=3.5, out.width='.5\\textwidth'>>=
load("data-25-25/unkn9.RData")
cmsdist <- sapply(reslist, function(x) x$maxCMS)

@@

\begin{figure}[hbtp]
  \centering
<<strange-res, echo=FALSE, fig.width=7, fig.height=3.25, out.width='.65\\textwidth', warning=FALSE>>=
load("data-25-25/unkn47.RData")
res <- reslist[[106]]
res$bullets$bullet <- scrubPath(res$bullets$bullet)

>>>>

\linenumbers
%\tableofcontents
%\newpage
<<setup, fig.keep='all', cache=FALSE, echo=FALSE, eval=TRUE, message=F, warning=F>>=
#rm(list=ls())
#wd <- getwd()
library(extrafont)
library(knitr)
imgdir <- "Figure/"
codedir <- "code"
datadir <- "images/Hamby (2009) Barrel/bullets"

options(replace.assign=TRUE,scipen=3, digits=2)
bstats <- read.csv("data/data-25-25/bullet-stats-old.csv")

@@

@@

\begin{figure}[hbtp]
  \centering
<<crosscuts-vary-b31, echo=FALSE, fig.width = 12, fig.height = 7, out.width = '\\textwidth', cache=TRUE, warning = FALSE>>=
paths <- file.path(datadir, dir(datadir))
paths <- paths[grep("Br[0-9]", paths)]

@@

\begin{figure}[hbtp]
\begin{subfigure}[t]{\textwidth}\centering
\caption{Maximal number of CMS between unknown bullet C-3 and all of the other 118 considered (known) lands. For two lands the number of maximum CMS is high. }
<<cms, echo=FALSE, fig.width=7, fig.height=3.5, out.width='.5\\textwidth'>>=
load("data/data-25-25/unkn9.RData")
cmsdist <- sapply(reslist, function(x) x$maxCMS)

@@

\begin{figure}[hbtp]
  \centering
<<strange-res, echo=FALSE, fig.width=7, fig.height=3.25, out.width='.65\\textwidth', warning=FALSE>>=
load("data/data-25-25/unkn47.RData")
res <- reslist[[106]]
res$bullets$bullet <- scrubPath(res$bullets$bullet)
